Demystifying the Computer Science \\ PhD Admission in the US\\{\large A Handbook for International \emph{and Domestic} Students

### 2024-10-30 demystify.tex
updates

But this is not why they ``ghost'' you and provide no response.  The main reason is that a response, no matter how generic, might be misinterpreted by the student.  For example, if they say they are not taking students but still (strongly) encourage you to apply, the student might take it as a positive sign of admission. Or if they say they are not interested, the student might take it as a personal rejection.

So it is safer to not reply at all.  This is why you should not take it personally if you do not get a reply.  It is not because profs. are busy, but because they are trying to avoid misunderstandings.

\begin{commentbox}{Vu: }
    I do scan through \emph{every single email} sent by students for admission and research opportunities (many of which are from undergrads and highschool students). However, I only reply to those that I think are a good fit and ask them to chat with me. 
    \end{commentbox}

>>>>

But this is not why they ``ghost'' you and provide no response.  It is because they are trying to avoid misunderstandings.  A response, no matter how generic, might be misinterpreted by the student.  For example, if they say they are not taking students but still (strongly) encourage you to apply, the student might take it as a positive sign of admission. Or if they say they are not interested, the student might take it as a personal rejection. So it is safer to not reply at all to avoid misunderstandings.

\begin{commentbox}{Vu: }
    I skim through \emph{every email} sent by students for admission and research opportunities (many of which are from undergrads and highschool students). So that means I do read your email, and it doesn't go to my spam/trash folder. 
    However, I only reply to those that I think are a good fit and ask them to chat with me.
    \end{commentbox}
